
---
output: # rmarkdown::github_document
  html_document:
  pdf_document: default
  word_document: default
title: "Assignment 3.  Working with Data Frame. Base R Style"
---

***Note*:** *This assignment practices working with Data Frame using Base R.*

***How to do it?***: 

- Open the Rmarkdown file of this assignment ([link](assignment3.Rmd)) in Rstudio. 

- Right under each question, insert  a code chunk (you can use the hotkey `Ctrl + Alt + I` to add a code chunk) and code the solution for the question. 

- `Knit` the rmarkdown file (hotkey: `Ctrl + Alt + K`) to export an html.  

-  Publish the html file to your Githiub Page. 

***Submission***: Submit the link on Github of the assignment to Canvas under Assignment 3. 

-------

Problems
-------
 \

1. Create the following data frame

| Rank 	| Age 	| Name  	|
|:------	|:-----	|:-------	|
| 0    	| 28  	| Tom   	|
| 1    	| 34  	| Jack  	|
| 2    	| 29  	| Steve 	|
| 3    	| 42  	| Ricky 	|
```{r}
df <- data.frame(Rank = c(0, 1, 2, 3),
                 Age = c(28, 34, 29, 42),
                 Name = c('Tom', 'Jack', 'Steve', 'Ricky'))
df
```

2. Use `read.csv` to import the Covid19 Vaccination data from WHO: [link](https://raw.githubusercontent.com/nytimes/covid-19-data/master/us-states.csv).
```{r}

covid_df <- read.csv('covid19data.csv')

```

2. Show the names of the variables in the data
```{r}
names(covid_df)
```

3. How many columns and rows the data have? 
```{r}
str(covid_df)
```

4. How many missing values are there?  Show the missing values by columns.  What variable has the most number of missing values?
```{r}
sum(is.na(covid_df))
```
```{r}
colSums(is.na(covid_df))
```
5. What is the class of the `date` column. Change the `date` columns to `date` type using the `as.Date` function. Show the new class of the `date` column. 
```{r}
class(covid_df$date)
```
```{r}
covid_df$date <- as.Date(covid_df$date)
str(covid_df)
```

6. Capitalize the names of all the variables
```{r}
names(covid_df) <- toupper(names(covid_df))
names(covid_df)
```

7. Find the average number of cases per day. Find the maximum cases a day.  
```{r}
mean(covid_df$CASES)
```
```{r}
max(covid_df$CASES)
```

8. How many states are there in the data?  
```{r}
length(unique(covid_df$STATE))
```
9. Create a new variable `weekdays` to store the weekday for each rows. 
```{r}
covid_df$weekdays <- weekdays(covid_df$DATE)
head(covid_df)
```
10. Create the categorical variable `death2` variable taking the values as follows

- `has_death` if there is a death that day
-  `no_death` if there is no death that day
```{r}
covid_df$death2 <- ifelse(covid_df$DEATHS > 0, 'has_death', 'no_death')
head(covid_df)
```

Find the frequency and relative frequency of `no_death` and `has_death`. 

```{r}
prop.table(table(covid_df$death2))
```
11. Find the first quartile (Q1), second quartile (Q2) and and third quartile (Q3) of the variable `death`. (Hint:  Use the `summary` function)
```{r}
summary(covid_df$DEATHS)
first_qu <- 1171 
third_qu <- 14912
```

12. Create the categorical variable `death3` variable taking the values as follows

- `low_death` if the number of deaths smaller than the 25 percentile (Q1)

- `mid_death` if the number of deaths from Q1 to Q3

- `high_death` if the number of deaths greater than Q3

```{r}
library(dplyr)
covid_df$death3 <- case_when(covid_df$DEATHS<first_qu ~ 'low_death',
                             covid_df$DEATHS<third_qu ~ 'mid_death',
                             TRUE~'high_death')
table(covid_df$death3)
```

13. Find the average cases in Rhode Island in 2021
```{r}
ri_df <- covid_df[covid_df$STATE == "Rhode Island",]
mean(ri_df$CASES)
```
14. Find the median cases by weekdays in Rhode Island in 2021 
```{r}
by(ri_df$CASES, ri_df$weekdays, median)
```
15. Compare the median cases in Rhode Island in June, July, August and September in 2021. 
```{r}
ri_df$year <- format(as.Date(ri_df$DATE, format="%d/%m/%Y"),"%Y") 
ri_df$month <- months(ri_df$DATE)
months = c("June", "July", "August")
ri_df_2021 <- ri_df[ri_df$year == 2021 &
                    ((ri_df$month == "June") |
                    (ri_df$month == "July") |
                    (ri_df$month == "August")),]
by(ri_df_2021$CASES, ri_df_2021$month, median)
```
16.  Find your own dataset, import it and implement the following functions on the data

- head
- str
- names
- mean, min, max
- table
- is.na
- colSums
- class
- cor
- by
- ifelse
- case_when

Importing Titanic DF
```{r}
titanic_df <- read.csv("titanic.csv")
head(titanic_df)
```
Inspecting Feature Names
```{r}
names(titanic_df)
```
Identifying dataframe data types and strcutre
```{r}
str(titanic_df)
```
Calulating Null Value Counts Per Feature
```{r}
colSums(is.na(titanic_df))
```

Changing Age Data Type, Dropping Null Values
```{r}
titanic_df$Age <- as.integer(titanic_df$Age)
titanic_df <- na.exclude(titanic_df)
```

Calculating Average Age for our Dataset
```{r}
mean(titanic_df$Age)
```
Minimum Age in Dataset
```{r}
min(titanic_df$Age)
```
Maximum Age in Dataset
```{r}
max(titanic_df$Age)
```
Correlation Between Features
```{r}
cor(titanic_df$Survived, titanic_df$Fare)
```
Mean Fare Passangers Paid Depending on Survival Outcome
```{r}
by(titanic_df$Fare, titanic_df$Survived, mean)
```
Changing Sex Feature to Numeric Dummy Value
```{r}
titanic_df$Sex <- ifelse(titanic_df$Sex == "female", 0, 1)
head(titanic_df$Sex)
```
Creating New Feature that Designates each Passenger into Age Grouping
```{r}
titanic_df$Age_Group <- case_when(titanic_df$Age<18 ~ '<18',
                             titanic_df$Age<=30 & titanic_df$Age >= 18 ~ '18 - 30',
                             titanic_df$Age>30 & titanic_df$Age <= 43 ~ '31 - 43',
                             titanic_df$Age>43 & titanic_df$Age <= 56 ~ '44 - 56',
                             TRUE~'>56')
```

17.  In the dataset in #16, practice the follows.  You can reuse the code of 16. 

- Create a categorical variable from a continuous variable
- From one categorical variable, create a new categorical variable with fewer categories

If you do not have a data, you can use [the titanic dataset](https://www.kaggle.com/competitions/titanic/overview), which can be downloaded at [this link](../data/titanic.csv)

Creating Categorical Variable from Continuous Variable
```{r}
titanic_df$Age_Group <- case_when(titanic_df$Age<18 ~ '<18',
                             titanic_df$Age<=30 & titanic_df$Age >= 18 ~ '18 - 30',
                             titanic_df$Age>30 & titanic_df$Age <= 43 ~ '31 - 43',
                             titanic_df$Age>43 & titanic_df$Age <= 56 ~ '44 - 56',
                             TRUE~'>56')
head(titanic_df$Age_Group)
```

Creating a Categorical Variable from Another with Fewer Categories
```{r}
titanic_df$Embarked <- ifelse(titanic_df$Embarked == "S" | titanic_df$Embarked == "C", "SC", "Q")
head(titanic_df$Embarked)
```

