
---
output: # rmarkdown::github_document
  html_document:
    theme: cerulean
    toc: true
  pdf_document: default
  word_document: default
title: "Assignment 5: Handle Missing Values"
---

***How to do it?***: 

- Open the Rmarkdown file of this assignment ([link](assignment5.Rmd)) in Rstudio. 

- Right under each **question**, insert  a code chunk (you can use the hotkey `Ctrl + Alt + I` to add a code chunk) and code the solution for the question. 

- `Knit` the rmarkdown file (hotkey: `Ctrl + Alt + K`) to export an html.  

-  Publish the html file to your Githiub Page. 

***Submission***: Submit the link on Github of the assignment to Canvas. 

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE)
```

-------

**The data:** 

This assignment works with the Adult Census Data that can be downloaded at [this link.](https://bryantstats.github.io/math421/data/adult_census_missing.csv)

-------

**Questions**

1. Use `read_csv` to import the data.  Show the number of NAs for each columns.   

```{r}
library('tidyverse')
df <- read_csv('adult_census_missing.csv')
colSums(is.na(df))
```
2. Using function `aggr` the VIM package to plot the number of NAs for each column. 

```{r}
library(VIM)
aggr(df)
```
3. Find other forms of missing values. Hint: You can use the `table` function to check if there are suspicious categories (Unknown, for example) in a variable. What all other forms of missing values shown in the data. 

```{r}
colSums(df=="?"|
        df=="Not Known" | 
        df=="Unknown", na.rm=TRUE)
```

4. Replace all the forms of missing values found to NA

```{r}
df_replace_nulls <- df %>%
  replace(df == "Unknown" |
          df == "Not Known" |
          df == "?", NA)
```
5. Replot the number of NAs for each column. 

```{r}
aggr(df_replace_nulls)

```


6. Approach 1 to handle NAs: remove all rows that have any NAs. Save the dataset after removing as a different data. The original data is unchanged (still have NAs).  How many rows left after removing?

```{r}
df_no_nulls <- drop_na(df_replace_nulls)
str(df_no_nulls)
```


7. Approach 2 to handle NAs:  Fill all the NAs with the previous or next value. (Hint: Using `fill` function).  Save the dataset after filling as a different data. The original data is unchanged (still have NAs). 

```{r}
df_filled_nas <- df_replace_nulls %>%
  fill(age, workclass, education, marital.status, 
       occupation, relationship, sex, 
       capital.gain, native.country, .direction = 'updown')

```


8. Approach 3 to handle NAs: For numeric variable, replace the NAs by the median.  For categorical variables, replace the NAs to the majority. 

```{r}
colSums(is.na(df_replace_nulls))

```
```{r}
df_replace_means <- df_replace_nulls

mean_age <- mean(df_replace_nulls$age, na.rm=TRUE)
df_replace_means$age <- replace_na(df_replace_means$age, mean_age)

mean_capgain <- mean(df_replace_means$capital.gain, na.rm=TRUE)
df_replace_means$capital.gain <- replace_na(df_replace_means$capital.gain, mean_capgain)

colSums(is.na(df_replace_means))
```

```{r}
majority_workclass <- names(which.max(table(df_replace_means$workclass)))
df_replace_means$workclass <- replace_na(df_replace_means$workclass, majority_workclass)

majority_education <- names(which.max(table(df_replace_means$education)))
df_replace_means$education <- replace_na(df_replace_means$education, majority_education)

majority_marital <- names(which.max(table(df_replace_means$marital.status)))
df_replace_means$marital.status <- replace_na(df_replace_means$marital.status, majority_marital)

majority_occupation <- names(which.max(table(df_replace_means$occupation)))
df_replace_means$occupation <- replace_na(df_replace_means$occupation, majority_occupation)

majority_relationship <- names(which.max(table(df_replace_means$relationship)))
df_replace_means$relationship <- replace_na(df_replace_means$relationship, majority_relationship)

majority_sex <- names(which.max(table(df_replace_means$sex)))
df_replace_means$sex <- replace_na(df_replace_means$sex, majority_sex)

majority_country <- names(which.max(table(df_replace_means$native.country)))
df_replace_means$native.country <- replace_na(df_replace_means$native.country, majority_country)
```

```{r}
colSums(is.na(df_replace_means))
```

```{r}
head(df_replace_means)
```










