---
output: # rmarkdown::github_document
  html_document:
  pdf_document: default
  word_document: default
title: "Assignment 4 - Extra Credits"
---

***How to do it?***:

-   Open the Rmarkdown file of this assignment ([link](assignment4_extra_credits.Rmd)) in Rstudio.

-   Right under each **question**, insert a code chunk (you can use the hotkey `Ctrl + Alt + I` to add a code chunk) and code the solution for the question.

-   Notice that if there is `eval=FALSE` in the first line of the code chunk, the chunk will not be execute.

-   `Knit` the rmarkdown file (hotkey: `Ctrl + Alt + K`) to export an html.

-   Publish the html file to your Githiub Page.

***Submission***: Submit the link on Github of the assignment to Canvas.

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE)
```

------------------------------------------------------------------------

This assignment works with the [IMDB Top 1000 data](../data/imdb_top_1000.csv). Find out more information about this data at [this link](https://www.kaggle.com/datasets/harshitshankhdhar/imdb-dataset-of-top-1000-movies-and-tv-shows). Import the data and answer the following questions.

```{r}
library(tidyverse)
df <- read_csv('imdb_top_1000.csv')
```

1.  List all the names of the columns of the data

```{r}
names(df)
```

2.  Which movies have the highest money earned (Gross)?

```{r}
df %>%
  select(Series_Title, Gross) %>%
  arrange(-Gross)
```

3.  What is the lowest rating (IMDB_Rating)? List five movies have this lowest rating.

```{r}
min(df$IMDB_Rating)
```

```{r}
df %>%
  filter(IMDB_Rating == 7.6) %>%
  select(Series_Title) %>%
  head(5)
```

4.  Which year have the most number of movies released in the list? What is the total of money earned on that year?

```{r}
df %>%
  group_by(Released_Year) %>%
  count() %>%
  arrange(-n)
```

```{r}
df %>%
  filter(Released_Year == "2014") %>%
  summarise(sum(Gross, na.rm = TRUE))
```

5.  What is the total money earned per movies on average?

```{r}
df %>%
  summarise(mean(Gross, na.rm = TRUE))
```

6.  Calculate the average number of votes by year. Calculate the average number of votes of movies that have IMDB rating greater than 9.

```{r}
df %>%
  group_by(Released_Year) %>%
  summarise(mean_votes = mean(No_of_Votes)) %>%
  arrange(-mean_votes)
```

```{r}
df %>%
  filter(IMDB_Rating > 9) %>%
  group_by(Released_Year) %>%
  summarise(mean_votes = mean(No_of_Votes)) %>%
  arrange(-mean_votes)
```

7.  Calculate the average Meta score in 2020 of movies that have number of votes in the third quartile.

```{r}
# There are no movies that are in the third quandrant for overall meta data in the year 2020
# Therefore I have decided to use the third quandrant for scores only in the year 2020
df_2020 <- df %>%
  filter(Released_Year == 2020)

summary(df_2020$No_of_Votes)
third_q <- 106083

df_2020 %>%
  filter(No_of_Votes > third_q) %>%
  summarise(mean(Meta_score, na.rm=TRUE))
```

8.  (Optional - Challenging). The current `Runtime` variable is not a numeric. Use the `str_remove` function to remove `min` from the variables then use `as.numeric` to convert the variable to numeric. Calculate the average running time in the 2010s. Calculate the correlation between running time and rating (adding `use="complete.obs"` in the `cor` function to ignore the missing values).

```{r}
df$Runtime <- str_remove(df$Runtime, " min")
```

```{r}
df$Runtime <- as.numeric(df$Runtime)
```

```{r}
df %>%
  filter(Released_Year > 2009 & Released_Year < 2020) %>%
  summarise(mean(Runtime))
```

```{r}
df$Released_Year <- as.integer(df$Released_Year)
cor(df$Runtime, df$Released_Year, use="complete.obs")
```

9.  We can use `select_if` to select columns satisfying a condition and use `summarise_if` to do calculation on columns satisfying a condition. Try the follows to understand these functions.

```{r,eval=FALSE}
# Select only character columns
df %>% select_if(is.character)

# Calculate the median of all numeric columns
df %>% summarise_if(is.numeric, mean, na.rm=TRUE)
```

10. Implement the follows functions or combos. Drawing a comment or summary from each calculation. The codes in this question should be different from the codes used in other questions.

-   select
-   filter
-   mutate
-   summarise
-   arrange
-   count
-   count + arrange
-   filter + count + arrange
-   group_by + summarise
-   filter + group_by + summarise
-   filter + group_by + summarise + arrange

Importing Dataframe
```{r}
df_2 <- read_csv('imdb_top_1000.csv')
head(df_2)
```

Selecting title, Rating, Meta score, and Gross total
```{r}
df_2 %>%
  select(Series_Title, IMDB_Rating, Meta_score, Gross)
```

Filtering only by movies that are scored 85, or 8.5 rating or meta score wise
```{r}
df_2 %>%
  filter(IMDB_Rating > 8.5, Meta_score > 85)
```

Creating a new column to calculate differnce between Rating and Meta Scores
```{r}
rateCompare <- df_2 %>%
  mutate(ratingVscore = (IMDB_Rating * 10) - Meta_score)

head(rateCompare$ratingVscore)
```

Calculating mean, max, min and the deviation between differences
```{r}
rateCompare %>%
  summarise(mean(ratingVscore, na.rm=TRUE), 
            max(ratingVscore, na.rm=TRUE), 
            min(ratingVscore, na.rm=TRUE),
            sd(ratingVscore, na.rm=TRUE))

# mean difference between ratings is only 1.3
# max result illustrates that we have large outliers
# High deviation: 11.9
```

Displaying count of movies where their IMDB rating and Meta score are the same
```{r}
rateCompare %>%
  filter(ratingVscore == 0) %>%
  count()
```

Displaying count of each genre in our dataset, largest to smallest
```{r}
df %>%
  group_by(Genre) %>%
  count() %>%
  arrange(-n)

# Large portion of our dataset is some sort of Drama or Romance genre 
```

Displaying counts of each genre for only movies with ratings of 9 or higher
```{r}
df %>%
  filter(IMDB_Rating >= 9) %>%
  group_by(Genre) %>%
  count() %>%
  arrange(-n)

# Only 5 movies with a rating greater than or equal to 9
# All 3 have drama as a genre
# 2 have crime
```

Displaying mean ratings for each genre of movie
```{r}
df %>%
  group_by(Genre) %>%
  summarise(mean_rating = mean(IMDB_Rating))
```

Displaying mean ratings for genres with movies greater than 8.3
```{r}
df %>%
  group_by(Genre) %>%
  summarise(mean_rating = mean(IMDB_Rating)) %>%
  filter(mean_rating > 8.3)

# 5 genres have an average rating greater than 8.3
```

Displaying mean ratings for genres with movies greater than 8.3, largest to smallest
```{r}
df %>%
  group_by(Genre) %>%
  summarise(mean_rating = mean(IMDB_Rating)) %>%
  filter(mean_rating > 8.3) %>%
  arrange(-mean_rating)

# Animation, Drama, War movies have best average rating for their movies
```
