
---
output: 
  html_document:
  pdf_document: default
  word_document: default
title: "Assignment 9: Visualization - Revealing a graph"
---

***How to do it?***: 

- Open the Rmarkdown file of this assignment ([link](assignment9.Rmd)) in Rstudio. 

- Right under each **question**, insert  a code chunk (you can use the hotkey `Ctrl + Alt + I` to add a code chunk) and code the solution for the question. 

- `Knit` the rmarkdown file (hotkey: `Ctrl + Alt + K`) to export an html.  

-  Publish the html file to your Githiub Page. 

***Submission***: Submit the link on Github of the assignment to Canvas

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE)
```


-------

**Notice:** *In this assignment, all the plot should have title, caption, and axis labels. *

1. Use the dataset by of covid 19 by WHO at https://covid19.who.int/WHO-COVID-19-global-data.csv. Find the three countries with the most numbers of deaths by Covid-19.

```{r}
library(tidyverse)
df <- read_csv('https://covid19.who.int/WHO-COVID-19-global-data.csv')

```

```{r}
df_top3 <- df %>% 
  filter(Date_reported == max(Date_reported)) %>%
  arrange(-Cumulative_deaths) %>%
  top_n(3)

head(df_top3)
  
```


Hint: 

-  Use `filter` to select the most current date 

-  Pipe with `arrange(-Cumulative_deaths)` to rank the data by the number of cumulative deaths


2. Use `transition_reveal` to make a plot revealing the number of deaths in the three countries with the most numbers of deaths

```{r}
library(ggplot2)
library(gganimate)
library(lubridate)
library(dplyr)

top_3 <- c('US', 'BR', 'IN')

df %>%
  filter(Country_code %in% top_3) %>%
  ggplot(aes(x=Date_reported, y=Cumulative_deaths, color=Country)) +
  geom_line() + 
  transition_reveal(Date_reported) +
  labs(title = 'Top 3 Countries COVID-19 Death Count',
       x = 'Date',
       y = 'Deaths',
       caption = 'US has high the highest number of recorded deaths.')
```

3. Create the new variable (column) `death_per_cases` recording the number of deaths per cases (Hint: divide cumulative deaths by cumulative cases).  What are the three countries with the highest deaths per cases? 

```{r}
df_deathsCase <- df %>%
  mutate(death_per_cases = Cumulative_deaths/Cumulative_cases)

df_deathsCase %>%
  filter(Date_reported == max(Date_reported)) %>%
  select(Country, death_per_cases) %>%
  arrange(-death_per_cases) %>%
  top_n(3)
  
```


4. Use `transition_reveal` to make a plot revealing the number of deaths per cases of the US, Italy and Mexico. 

```{r}
selected <- c('US', 'IT', 'MX')

df_deathsCase %>%
  filter(Country_code %in% selected) %>%
  mutate(death_per_cases = replace_na(death_per_cases, 0)) %>%
  ggplot(aes(x=Date_reported, y=death_per_cases, color=Country)) +
  geom_line() + 
  transition_reveal(Date_reported) +
  labs(title = 'COVID-19 Death per Case Count',
       x = 'Date',
       y = 'Deaths per Case',
       caption = 'Italy has high the highest recorded ratio.')
```


5. Import the following data https://raw.githubusercontent.com/owid/covid-19-data/master/public/data/vaccinations/vaccinations.csv

```{r}
df2 <- read_csv('https://raw.githubusercontent.com/owid/covid-19-data/master/public/data/vaccinations/vaccinations.csv')

head(df2)
```

                      
Use `transition_reveal` to plot the total vaccinations per hundred by level of income. Hint: the levels of income are identified in the `location` variable. Put a short comment on the caption of the plot. 

```{r}
income <- c('High income', 'Lower middle income', 'Upper middle income', 'Low income')

df2 %>%
  filter(location %in% income) %>%
  ggplot(aes(x=date, y=total_vaccinations_per_hundred, color=location)) +
  geom_line() + 
  transition_reveal(date) +
  labs(title = 'Total Vaccinations per 100 People by Income Level',
       x = 'Date',
       y = 'Vaccinations per 100',
       caption = 'High and Upper middle income have higher vaccination rates')
  
```

