
---
output: 
  html_document:
  pdf_document: default
  word_document: default
title: "Assignment 7 - Extra Credits: Practice dplyr and ggplot2"
---

***How to do it?***: 

- Open the Rmarkdown file of this assignment ([link](assignment7_extra_credits.Rmd)) in Rstudio. 

- Right under each **question**, insert  a code chunk (you can use the hotkey `Ctrl + Alt + I` to add a code chunk) and code the solution for the question. 

- `Knit` the rmarkdown file (hotkey: `Ctrl + Alt + K`) to export an html.  

-  Publish the html file to your Githiub Page. 

***Submission***: Submit the link on Github of the assignment to Canvas



```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE, warning = FALSE)
```

-------

1. Import the data at https://bryantstats.github.io/math421/data/ds_salaries.csv

    The data description can be found at https://www.kaggle.com/datasets/saurabhshahane/data-science-jobs-salaries
    
```{r}
library(tidyverse)
df <- read_csv('https://bryantstats.github.io/math421/data/ds_salaries.csv')
```

2. Is there any column that contains NAs?

```{r}
# No columns have any null values
colSums(is.na(df))
```
3. What is the most frequent job title in the data?

```{r}
# Data Scientist
df %>%
  group_by(job_title) %>%
  count() %>%
  arrange(-n) %>%
  head(3)
```

4. Find the average salary data of the three most frequent job titles in the data. 

```{r}
df %>%
  filter(job_title == "Data Scientist" |
         job_title == "Data Engineer" |
         job_title == "Data Analyst") %>%
  group_by(job_title) %>%
  summarise(mean_salary = mean(salary_in_usd, na.rm=TRUE)) %>%
  arrange(-mean_salary)
```

5. What is the job title that have the highest average salary?

```{r}
# Data Analytics Lead
df %>%
  group_by(job_title) %>%
  summarise(mean_salary = mean(salary_in_usd)) %>%
  arrange(-mean_salary) %>%
  head(1)
```

6. Which country gives the highest salary on average? 

```{r}
# Russia
df %>%
  group_by(company_location) %>%
  summarise(mean_salary = mean(salary_in_usd)) %>%
  arrange(-mean_salary) %>%
  head(1)
```

7. Plot five meaningful plots. All plots should have title, caption, and appropriate labels.

```{r}
df_plot_1 <- df %>%
  filter(job_title == "Data Scientist" |
         job_title == "Data Engineer" |
         job_title == "Data Analyst") %>%
  group_by(job_title) %>%
  summarise(mean_sal = mean(salary_in_usd)) %>%
  ggplot() +
  geom_bar(mapping = aes(x = job_title, y = mean_sal), stat = "identity") + 
  labs(x = 'Job Title',
       y = 'Mean Salary',
       title = 'Top 3 Most Frequent Jobs Average Salary',
       caption = 'Top 3 Jobs Listed in Current Dataset.')

show(df_plot_1)
```

```{r}
df_dateeng <- df %>% filter(job_title == "Data Engineer") %>%
  group_by(work_year) %>%
  summarise(mean_DE_sal = mean(salary_in_usd))

df_datesci <- df %>% filter(job_title == "Data Scientist") %>%
  group_by(work_year) %>%
  summarise(mean_DS_sal = mean(salary_in_usd))

df_dateana <- df %>% filter(job_title == "Data Analyst") %>%
  group_by(work_year) %>%
  summarise(mean_AN_sal = mean(salary_in_usd))

df_alljobs <- df %>% filter(job_title != "Data Scientist" &
                     job_title != "Data Analyst" &
                     job_title != "Data Engineer") %>%
  group_by(work_year) %>%
  summarise(mean_alljobs_salary = mean(salary_in_usd))

merged_df <- df_alljobs %>%
  merge(df_dateana, by='work_year', all=TRUE) %>%
  merge(df_dateeng, by='work_year', all=TRUE) %>%
  merge(df_datesci, by='work_year', all=TRUE)

df_plot_2 <- ggplot(merged_df, aes(x = work_year)) +
  geom_line(aes(y = mean_alljobs_salary, color = "All Other Jobs"), linetype = "dashed") +
  geom_line(aes(y = mean_AN_sal, color = "Data Analyst")) +
  geom_line(aes(y = mean_DE_sal, color = "Data Engineer")) +
  geom_line(aes(y = mean_DS_sal, color = "Data Scientist")) +
  labs(x='Year',
       y='Mean Salary',
       title='Average Data Engineer Salary by Year',
       caption='Data Engineering having the highest average salary among the three most commonly listed jobs.')+
  scale_x_continuous(breaks = seq(2020, 2022, by = 1))

show(df_plot_2)
```

```{r}
df %>% ggplot() +
  geom_histogram(mapping = aes(x=salary_in_usd)) +
  labs(x = 'Salary',
       y = 'Count',
       title = 'Salary Distribution for Dataset',
       caption = 'Distribution illustrtaes majority of salaries are within $200,000.')
```

```{r}
df %>%
  group_by(company_size) %>%
  summarise(mean_salary = mean(salary_in_usd)) %>%
  ggplot() + 
  geom_bar(mapping = aes(x = company_size, y = mean_salary), stat = "identity") +
  labs(x = 'Company Size',
       y = 'Mean Salary',
       title = 'Mean Salary by Company Size',
       caption = 'Large, medium sized companies hold a very similar average salary.')
```
```{r}
head(df)

df %>%
  group_by(company_size, employment_type) %>%
  summarise(mean_salary = mean(salary_in_usd)) %>%
  ggplot() + 
  geom_bar(mapping = aes(x = company_size, y = mean_salary, fill=employment_type), 
           stat = "identity", position='dodge') + 
  labs(x='Company Size',
       y='Salary',
       title='Salary by Company Size, Employment Type',
       caption = 'CT employment holds a larger average salary for smaller companies.')
```



