
---
title: "Adult Census Data"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    source_code: embed
    social: menu
---

```{r setup, include=FALSE}
library(flexdashboard)
library(tidyverse)
library(plotly)
library(knitr)
library(DT)
df <- read_csv('adult_census_missing.csv')

# Create a ggplot object
p <- df %>%
  filter(education != "NA", education != "Not Known", education != "Unknown") %>%
  group_by(education, income) %>%
  count() %>%
  arrange(-n) %>%
  ggplot(aes(y = education, x = n, fill = income)) +
  geom_bar(stat = 'identity') +
  labs(x = 'Count', 
       y = 'Education Level')

p1 <- df %>%
  group_by(income, sex) %>%
  count() %>%
  arrange(-n) %>%
  ggplot(aes(x = income, y = n, fill = sex)) +
  geom_bar(stat = 'identity') +
  labs(x = 'Income Level', 
       y = 'Count')

p2 <- df %>%
  filter(education != "NA", education != "Not Known", education != "Unknown") %>%
  group_by(race, income) %>%
  count() %>%
  arrange(-n) %>%
  ggplot(aes(y = race, x = n, fill = income)) +
  geom_bar(stat = 'identity') +
  labs(x = 'Count', 
       y = 'Race')
```

{.sidebar}
=======================================================================

### 1. Brief Dataset Description

This dataset includes personal census data for individuals such as, age, workclass, education, marital staus and income. 

### 2. Flexdashboard and Plotly

This interactive uses `flexdashboard` and `plotly` to visualize the data. 

Main Tab 1
=======================================================================

Column {data-width=500, .tabset}
-----------------------------------------------------------------------

### Raw Income Data

```{r}
df$income
```


### Raw Dataset

```{r}
df
```


### Formatted Dataset

```{r}
datatable(df, options = list(
  pageLength = 25
))
```


Column {data-width=750}
-----------------------------------------------------------------------

### Income Distribution by Sex

```{r}
p1
```

### Interactive Visual

```{r}
ggplotly(p1)
```


Main Tab 2
=======================================================================

Column {data-width=500}
-----------------------------------------------------------------------

### Education Distribution by Income

```{r}
p
```

### Interactive Visual

```{r}
ggplotly(p)
```

Main Tab 3
=======================================================================

Column {data-width=500}
-----------------------------------------------------------------------

### Education Distribution by Income

```{r}
p2
```

### Interactive Visual

```{r}
ggplotly(p2)
```


